---
title: "xos_ms_dataandcode"
author: "Zofia Tillman"
date: "`r Sys.Date()`"
output:
  github_document:
    html_preview: false
---

Data and code used to run analysis and create visualizations/tables for 'Rapid measurement of soluble xylo-oligomers using near-infrared spectroscopy (NIRS) and multivariate statistics: calibration model
development and practical approaches to model optimization' (Biotechnology for Biofuels and Bioproducts 2024, https://doi.org/10.1186/s13068-024-02558-6)

## How to Reproduce Analysis

1. Open R studio and change to version 4.2.3 via *Tools -> Global Options -> R version -> Change...*
3. In R studio, source,  `./code/runAnalysis.R` 

```{r library_calls, message=FALSE, echo=FALSE, warning = FALSE}
library(tidyverse)
library(pls)
library(prospectr)
library(ggfortify)
library(ggpmisc)
library(openxlsx)
library(ggh4x)
library(ggmagnify)
library(egg)
library(patchwork)
```
## Dependencies

* `r R.version.string`
  * `tidyverse` (v. `r packageVersion("tidyverse")`)
  * `pls` (v. `r packageVersion("pls")`)
  * `prospectr` (v. `r packageVersion("prospectr")`)
  * `ggfortify` (v. `r packageVersion("ggfortify")`)
  * `ggpmisc` (v. `r packageVersion("ggpmisc")`)
  * `rmarkdown` (v. `r packageVersion("rmarkdown")`)
  * `openxlsx` (v. `r packageVersion("openxlsx")`)
  * `ggh4x` (v. `r packageVersion("ggh4x")`)
  * `ggmagnify` (v. `r packageVersion("ggmagnify")`)
  * `patchwork` (v. `r packageVersion("patchwork")`)
  * `egg` (v. `r packageVersion("egg")`)
  

## My Computer
```{r sessioninfo, echo=FALSE}
sessionInfo()
```